Databases are an effective and efficient method for storage and access of mass-spectrometry data

### 2025-02-27 manuscript/manuscript.Rmd
Cleaning up conversion code

msconvert *.raw --filter "peakPicking true 1-" --filter "polarity positive" 
msconvert *.raw --mzMLb --filter "peakPicking true 1-" --filter "polarity positive" 
msconvert *.raw --mz5 --filter "peakPicking true 1-" --filter "polarity positive"
for %f in (*.raw) do "C:\Program Files\ProteoWizard\raw2mzDB_0.9.10_build20170802\raw2mzDB.exe" -i %f -c 1-2 --safeMode
for %f in (*.mzML) do mza.exe -file %f
```

>>>>

# After adding msconvert, raw2mzdb, and mza executables to PATH:
msconvert 20220921_LEAP-POS_BL01.raw --filter "peakPicking true 1-"
msconvert 20220921_LEAP-POS_BL01.raw --mzMLb --filter "peakPicking true 1-"
msconvert 20220921_LEAP-POS_BL01.raw --mz5 --filter "peakPicking true 1-"
raw2mzDB -i 20220921_LEAP-POS_BL01.raw  -c 1-2 --safeMode
mza -file 20220921_LEAP-POS_BL01.raw
```
